---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rainbowr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/djnavarro/rainbowr.svg?branch=master)](https://travis-ci.org/djnavarro/rainbowr)
<!-- badges: end -->

The `rainbowr` package generates LGBT pride flags overlaid with the R logo

## Installation

The package can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("djnavarro/rainbowr")
```
## Example 1: LGBT banners

```{r example}
library(magick)
library(rainbowr)

rainbow_flag <- make_banner("rainbow")
plot(rainbow_flag)

trans_flag <- make_banner("transgender")
plot(trans_flag)
```

The flags are taken from the Wikipedia page for [LGBT symbols](https://en.wikipedia.org/wiki/LGBT_symbols) and the Wikicommons page for [Sexual identity symbols](https://commons.wikimedia.org/wiki/Sexual_identity_symbols), but is not exhaustive. To see which flags are included:

```{r flag_list}
list_flags()
```


## Example 2: LGBT hexes

```{r example2}
rainbow_hex <- make_hex("rainbow")
plot(rainbow_hex)

trans_hex <- make_hex("transgender", palette = c("grey50", "black"))
plot(trans_hex)
```

## Example 3: Tiled LGBT hexes


```{r example 3}
df <- data.frame(
  flag = c("rainbow", "transgender", "bisexual", "bear", "aromantic", "lesbian"),
  palette1 = c("white", "grey80", "#ccccff", "grey30", "grey50", "grey50"),
  palette2 = c("black", "black", "white", "brown", "black", "lavender"),
  row = c(1, 1, 2, 3, 3, 2),
  col = c(1, 2, 1, 2, 3, 3),
  stringsAsFactors = FALSE
)

hextile <- make_hextile(df)
plot(hextile)
```



